### 2021-04-09 end_appendix/appendix.tex
Removed nameref*

@@

\begin{table}[!h]
  \centering
  \begin{tabulary}{\columnwidth}{>{\em}L L}
    \toprule
    \ignorecolumntype{l}{Variable short name} & Description \\
    \midrule
    cl & Cloud area fraction \\
    clt & Total cloud area fraction \\
    hur & Relative humidity \\
    hus & Specific humidity \\
    pr & \Acl{PR} \\
    rsdt & \Acf{TOA} incoming shortwave radiation \\
    rsut & \acs{TOA} outgoing shortwave radiation \\
    rsutcs & Clear-sky \acs{TOA} outgoing shortwave radiation \\
    ta & Air temperature \\
    tas & Surface air temperature \\
    tos & Sea surface temperature \\
    ts & Surface temperature \\
    va & Northward wind speed \\
    wap & Vertical velocity \\
    \bottomrule
  \end{tabulary}
  \caption[
    Overview of the variables used in \cref{ch:05:paper_ecs}.
  ]{
    Overview of the variables used in \cref{ch:05:paper_ecs}
    (\nameref*{ch:05:paper_ecs}). More details are given in
    \cref{tab:05:overview_emergent_constraints}, which lists the variables used
    for each emergent constraint.
  }
  \label{tab:app:a:overview_variables}
\end{table}

\begin{table}[!b]
  \centering
  \begin{tabulary}{\columnwidth}{L >{\em}L L}
    \toprule
    Observational dataset & \ignorecolumntype{l}{Corresponding variables} &
    Reference \\
    \midrule
    AIRS & hur, hus & \textcite{Aumann2003} \\
    AMSRE \acs{SST} & tos & \textcite{AMSRE2011} \\
    CERES-EBAF & rsdt, rsut, rsutcs & \textcite{Loeb2018} \\
    CloudSat/CALIPSO & cl & \textcite{Mace2009} \\
    ERA-Interim & hur, ta, va, wap & \textcite{Dee2011} \\
    GPCP & pr & \textcite{Adler2003} \\
    HadCRUT4 & tas & \textcite{Morice2012} \\
    HadISST & ts & \textcite{Rayner2003} \\
    ISCCP D-2 & clt & \textcite{Rossow1991} \\
    MLS-Aura & hur & \textcite{Beer2006} \\
    \bottomrule
  \end{tabulary}
  \caption[
    References for all observational datasets used in \cref{ch:05:paper_ecs}.
  ]{
    References for all observational datasets used in \cref{ch:05:paper_ecs}
    (\nameref*{ch:05:paper_ecs}). More details are given in
    \cref{tab:05:overview_emergent_constraints}, which lists the observational
    datasets used for each emergent constraint.
  }
  \label{tab:app:a:observations}
\end{table}

\begin{table}[p]
  \centering
  \begin{tabulary}{\columnwidth}{L >{$}L<{$} L}
    \toprule
    Model & \ignorecolumntype{l}{Index} & Main reference \\
    \midrule
    ACCESS1-0 & 1 & \textcite{Dix2013} \\
    ACCESS1-3 & 2 & \textcite{Dix2013} \\
    BNU-ESM & 3 & \textcite{Ji2014} \\
    CCSM4 & 4 & \textcite{Gent2011, Meehl2012} \\
    CNRM-CM5 & 5 & \textcite{Voldoire2013} \\
    CNRM-CM5-2 & 6 & \textcite{Voldoire2013} \\
    CSIRO-Mk3-6-0 & 7 & \textcite{Rotstayn2012} \\
    CanESM2 & 8 & \textcite{Arora2011} \\
    FGOALS-g2 & 9 & \textcite{Li2013} \\
    GFDL-CM3 & 10 & \textcite{Donner2011} \\
    GFDL-ESM2G & 11 & \textcite{Dunne2012} \\
    GFDL-ESM2M & 12 & \textcite{Dunne2012} \\
    GISS-E2-H & 13 & \textcite{Schmidt2006} \\
    GISS-E2-R & 14 & \textcite{Schmidt2006} \\
    \acs{HadGEM}2-ES & 15 & \textcite{Collins2011} \\
    IPSL-CM5A-LR & 16 & \textcite{Dufresne2013} \\
    IPSL-CM5A-MR & 17 & \textcite{Dufresne2013} \\
    IPSL-CM5B-LR & 18 & \textcite{Dufresne2013} \\
    MIROC-ESM & 19 & \textcite{Watanabe2011} \\
    MIROC5 & 20 & \textcite{Watanabe2010} \\
    MPI-ESM-LR & 21 & \textcite{Giorgetta2013} \\
    MPI-ESM-MR & 22 & \textcite{Giorgetta2013} \\
    MPI-ESM-P & 23 & \textcite{Giorgetta2013} \\
    MRI-CGCM3 & 24 & \textcite{Yukimoto2012} \\
    NorESM1-M & 25 & \textcite{Bentsen2013, Iversen2013} \\
    bcc-csm1-1 & 26 & \textcite{Wu2014} \\
    bcc-csm1-1-m & 27 & \textcite{Wu2014} \\
    inmcm4 & 28 & \textcite{Volodin2010} \\
    \bottomrule
  \end{tabulary}
  \caption[
    List of \acs{CMIP}5 models used in \cref{ch:05:paper_ecs}.
  ]{
    List of \acs{CMIP}5 models used in \cref{ch:05:paper_ecs}
    (\nameref*{ch:05:paper_ecs}) alongside the main reference and the index
    used in the corresponding figures. \AdaptedFrom{Schlund2020a}.
  }
  \label{tab:app:a:cmip5_models}
\end{table}

@@

\begin{table}[p]
  \centering
  \csvreader[EmergentConstraintsPart1Table]{
    ch05_paper_ecs/data/cmip5_emergent_constraints.csv}{}{
    \dataset & $\idx$ & $\ECS$ & $\BRI$ & $\COX$ & $\LIP$ & $\SHD$ & $\SHL$ &
    $\SHS$}
  \caption[
    All \acs{CMIP}5 models used in \cref{ch:05:paper_ecs} including their
    \acf{ECS} and \xaxis{} values for the emergent constraints BRI, COX, LIP,
    SHD, SHL, and SHS.
  ]{
    All \acs{CMIP}5 models used in \cref{ch:05:paper_ecs}
    (\nameref*{ch:05:paper_ecs}) including their \acf{ECS} and \xaxis{} values
    for the emergent constraints BRI, COX, LIP, SHD, SHL, and SHS. More details
    on the emergent constraints are given in
    \cref{tab:05:overview_emergent_constraints}. The specified index
    corresponds to the index used in the associated figures.
    \AdaptedFrom{Schlund2020a}.
  }
  \label{tab:app:a:cmip5_emergent_constraints_part1}
\end{table}

@@

\begin{table}[p]
  \centering
  \begin{tabulary}{\columnwidth}{L L L}
    \toprule
    Climate model & Land model & Main reference \\
    \midrule
    \acs{CESM}1-BGC & CLM4 & \textcite{Gent2011} \\
    CanESM2 & CLASS2.7 + CTEM1 & \textcite{Arora2011} \\
    GFDL-ESM2M & LM3 & \textcite{Dunne2012} \\
    \acs{HadGEM}2-ES & JULES + TRIFFID & \textcite{Collins2011} \\
    MIROC-ESM & MATSIRO + SEIB-DGVM & \textcite{Watanabe2011} \\
    MPI-ESM-LR & JSBACH + BETHY & \textcite{Giorgetta2013} \\
    NorESM1-ME & CLM4 & \textcite{Iversen2013} \\
    \bottomrule
  \end{tabulary}
  \caption[
    List of the seven \acs{CMIP}5 models used in \cref{ch:06:paper_gpp}
    alongside the main references.
  ]{
    List of the seven \acs{CMIP}5 models used in \cref{ch:06:paper_gpp}
    (\nameref*{ch:06:paper_gpp}) alongside the main references. More details
    are given by \textcite{Anav2013}. We chose all \acs{CMIP}5 models which
    provide all necessary variables (\emph{co2}, \emph{gpp}, \emph{lai},
    \emph{pr}, \emph{rsds}, and \emph{tas}) for all used experiments
    (\emph{esmHistorical}, \emph{esmrcp85}, and \emph{esmFixClim1}). For all
    models, we only use the first ensemble member available.
    \AdaptedFrom{Schlund2020}.
  }
  \label{tab:app:b:cmip5_models}
\end{table}

>>>>

\vspace{7mm}

\begin{table}[!h]
  \centering
  \begin{tabulary}{\columnwidth}{>{\em}L L}
    \toprule
    \ignorecolumntype{l}{Variable short name} & Description \\
    \midrule
    cl & Cloud area fraction \\
    clt & Total cloud area fraction \\
    hur & Relative humidity \\
    hus & Specific humidity \\
    pr & \Acl{PR} \\
    rsdt & \Acf{TOA} incoming shortwave radiation \\
    rsut & \acs{TOA} outgoing shortwave radiation \\
    rsutcs & Clear-sky \acs{TOA} outgoing shortwave radiation \\
    ta & Air temperature \\
    tas & Surface air temperature \\
    tos & Sea surface temperature \\
    ts & Surface temperature \\
    va & Northward wind speed \\
    wap & Vertical velocity \\
    \bottomrule
  \end{tabulary}
  \caption[
    Overview of the variables used in \cref{ch:05:paper_ecs}.
  ]{
    Overview of the variables used in \cref{ch:05:paper_ecs}. More details are
    given in \cref{tab:05:overview_emergent_constraints}, which lists the
    variables used for each emergent constraint.
  }
  \label{tab:app:a:overview_variables}
\end{table}

@@

\begin{table}[!b]
  \centering
  \begin{tabulary}{\columnwidth}{L >{\em}L L}
    \toprule
    Observational dataset & \ignorecolumntype{l}{Corresponding variables} &
    Reference \\
    \midrule
    AIRS & hur, hus & \textcite{Aumann2003} \\
    AMSRE \acs{SST} & tos & \textcite{AMSRE2011} \\
    CERES-EBAF & rsdt, rsut, rsutcs & \textcite{Loeb2018} \\
    CloudSat/CALIPSO & cl & \textcite{Mace2009} \\
    ERA-Interim & hur, ta, va, wap & \textcite{Dee2011} \\
    GPCP & pr & \textcite{Adler2003} \\
    HadCRUT4 & tas & \textcite{Morice2012} \\
    HadISST & ts & \textcite{Rayner2003} \\
    ISCCP D-2 & clt & \textcite{Rossow1991} \\
    MLS-Aura & hur & \textcite{Beer2006} \\
    \bottomrule
  \end{tabulary}
  \caption[
    References for all observational datasets used in \cref{ch:05:paper_ecs}.
  ]{
    References for all observational datasets used in \cref{ch:05:paper_ecs}.
    More details are given in \cref{tab:05:overview_emergent_constraints},
    which lists the observational datasets used for each emergent constraint.
  }
  \label{tab:app:a:observations}
\end{table}

\begin{table}[p]
  \centering
  \begin{tabulary}{\columnwidth}{L >{$}L<{$} L}
    \toprule
    Model & \ignorecolumntype{l}{Index} & Main reference \\
    \midrule
    ACCESS1-0 & 1 & \textcite{Dix2013} \\
    ACCESS1-3 & 2 & \textcite{Dix2013} \\
    BNU-ESM & 3 & \textcite{Ji2014} \\
    CCSM4 & 4 & \textcite{Gent2011, Meehl2012} \\
    CNRM-CM5 & 5 & \textcite{Voldoire2013} \\
    CNRM-CM5-2 & 6 & \textcite{Voldoire2013} \\
    CSIRO-Mk3-6-0 & 7 & \textcite{Rotstayn2012} \\
    CanESM2 & 8 & \textcite{Arora2011} \\
    FGOALS-g2 & 9 & \textcite{Li2013} \\
    GFDL-CM3 & 10 & \textcite{Donner2011} \\
    GFDL-ESM2G & 11 & \textcite{Dunne2012} \\
    GFDL-ESM2M & 12 & \textcite{Dunne2012} \\
    GISS-E2-H & 13 & \textcite{Schmidt2006} \\
    GISS-E2-R & 14 & \textcite{Schmidt2006} \\
    \acs{HadGEM}2-ES & 15 & \textcite{Collins2011} \\
    IPSL-CM5A-LR & 16 & \textcite{Dufresne2013} \\
    IPSL-CM5A-MR & 17 & \textcite{Dufresne2013} \\
    IPSL-CM5B-LR & 18 & \textcite{Dufresne2013} \\
    MIROC-ESM & 19 & \textcite{Watanabe2011} \\
    MIROC5 & 20 & \textcite{Watanabe2010} \\
    MPI-ESM-LR & 21 & \textcite{Giorgetta2013} \\
    MPI-ESM-MR & 22 & \textcite{Giorgetta2013} \\
    MPI-ESM-P & 23 & \textcite{Giorgetta2013} \\
    MRI-CGCM3 & 24 & \textcite{Yukimoto2012} \\
    NorESM1-M & 25 & \textcite{Bentsen2013, Iversen2013} \\
    bcc-csm1-1 & 26 & \textcite{Wu2014} \\
    bcc-csm1-1-m & 27 & \textcite{Wu2014} \\
    inmcm4 & 28 & \textcite{Volodin2010} \\
    \bottomrule
  \end{tabulary}
  \caption[
    List of \acs{CMIP}5 models used in \cref{ch:05:paper_ecs}.
  ]{
    List of \acs{CMIP}5 models used in \cref{ch:05:paper_ecs} alongside the
    main reference and the index used in the corresponding figures.
    \AdaptedFrom{Schlund2020a}.
  }
  \label{tab:app:a:cmip5_models}
\end{table}

@@

\begin{table}[p]
  \centering
  \csvreader[EmergentConstraintsPart1Table]{
    ch05_paper_ecs/data/cmip5_emergent_constraints.csv}{}{
    \dataset & $\idx$ & $\ECS$ & $\BRI$ & $\COX$ & $\LIP$ & $\SHD$ & $\SHL$ &
    $\SHS$}
  \caption[
    All \acs{CMIP}5 models used in \cref{ch:05:paper_ecs} including their
    \acf{ECS} and \xaxis{} values for the emergent constraints BRI, COX, LIP,
    SHD, SHL, and SHS.
  ]{
    All \acs{CMIP}5 models used in \cref{ch:05:paper_ecs} including their
    \acf{ECS} and \xaxis{} values for the emergent constraints BRI, COX, LIP,
    SHD, SHL, and SHS. More details on the emergent constraints are given in
    \cref{tab:05:overview_emergent_constraints}. The specified index
    corresponds to the index used in the associated figures.
    \AdaptedFrom{Schlund2020a}.
  }
  \label{tab:app:a:cmip5_emergent_constraints_part1}
\end{table}

@@

\begin{table}[p]
  \centering
  \begin{tabulary}{\columnwidth}{L L L}
    \toprule
    Climate model & Land model & Main reference \\
    \midrule
    \acs{CESM}1-BGC & CLM4 & \textcite{Gent2011} \\
    CanESM2 & CLASS2.7 + CTEM1 & \textcite{Arora2011} \\
    GFDL-ESM2M & LM3 & \textcite{Dunne2012} \\
    \acs{HadGEM}2-ES & JULES + TRIFFID & \textcite{Collins2011} \\
    MIROC-ESM & MATSIRO + SEIB-DGVM & \textcite{Watanabe2011} \\
    MPI-ESM-LR & JSBACH + BETHY & \textcite{Giorgetta2013} \\
    NorESM1-ME & CLM4 & \textcite{Iversen2013} \\
    \bottomrule
  \end{tabulary}
  \caption[
    List of the seven \acs{CMIP}5 models used in \cref{ch:06:paper_gpp}
    alongside the main references.
  ]{
    List of the seven \acs{CMIP}5 models used in \cref{ch:06:paper_gpp}
    alongside the main references. More details are given by
    \textcite{Anav2013}. We chose all \acs{CMIP}5 models which provide all
    necessary variables (\emph{co2}, \emph{gpp}, \emph{lai}, \emph{pr},
    \emph{rsds}, and \emph{tas}) for all used experiments
    (\emph{esmHistorical}, \emph{esmrcp85}, and \emph{esmFixClim1}). For all
    models, we only use the first ensemble member available.
    \AdaptedFrom{Schlund2020}.
  }
  \label{tab:app:b:cmip5_models}
\end{table}
